What is an Ancestral Recombination Graph?

### 2022-04-05 paper.tex
Update caption to fig 5 to match

\begin{figure}
\centering
\vspace{5em}
\includegraphics[width=\linewidth]{illustrations/simplification}
\caption{\label{fig-simplification}
ARG simplification. (A) An ARG simulated from a diploid Wright-Fisher
model. Note the complex full-sib relationship between B and C; this
could not be directly represented in a Griffiths-like EARG encoding
(see section XXX).
(B) Simplified to remove all
% trying out this terminology - can define in the text
1-connected graph components (e.g., diamonds).
(C) Remove nodes that are unary in all local trees.
(D) Rewrite edges to skip any unary nodes in local trees.
(E) The local trees for ARG (A).
(F) The local trees for ARG (D).
}
\end{figure}

>>>>

\begin{figure}
\centering
\vspace{5em}
\includegraphics[width=\linewidth]{illustrations/simplification}
\caption{\label{fig-simplification}
ARG simplification. In all cases the graph visualization is shown on the left
and the equivalent marginal trees on the right.
(A) An ARG simulated from a diploid Wright-Fisher
model. Note that the genome \textsf{K} has three children and the genomes
\textsf{E} and \textsf{G} simultaneously have multiple parents and multiple children;
neither could not be directly represented in a Griffiths-like EARG encoding
(see section XXX).
(B) Simplified to remove all
% trying out this terminology - can define in the text
1-connected graph components (e.g., diamonds such as \textsf{JLMN}).
(C) Remove nodes that are unary in all local trees. This removes both recombinant nodes
that have only one child (e.g. \textsf{N}) and nodes that have more
than one child (i.e. are ``common ancestors'') but never represent coalescences
in the local trees (e.g. \textsf{R}).
(D) Rewrite edges to bypass any unary nodes in local trees. Note that this loses lineage
information such as the fact that \textsf{K} is connected to \textsf{A} via \textsf{E}; it
can also create many extra roots.
}
\end{figure}
